\section{Conclusion}
\label{sec.conclusion}

\cappos{I feel we will really need a limitations section.  It's clear there
are a lot of things we could do to round out the work.  For example,
using other OSes for analysis (Windows, etc.), testing hypervisors, etc.
I do not know if it can be a subsection here, but it is worth being
very direct about. }

\cappos{On a similar note, we likely also need to be very clear about the
limitations / framing of the problem up front so the reader does not expect
more than we provide.}

Isolating untrusted user applications from the underlying kernel is
desirable, in order to protect the privileged code and 
avoid the exploitation of bugs. However, there has yet to be a standard
method that can shed lights on how to effectively
isolate the user space applications from the kernel space without losing
desired functionality.

We propose a new metric that quantitatively measures and evaluates the
kernel code being executed when running
user applications. We have a key hypothesis that commonly used kernel paths
contain few bugs. Using our metric, 
we have findings suggesting the hypothesis is reasonable and solid. 

A new design for building secure systems was created based on the findings
from our metric. 
We implemented a sandbox system, called Lind, which is based upon the new
design using our metric. 
Our system Lind, securely reconstruct complex yet essential OS
functionality inside a sandbox. 
The sandbox itself is designed to have a minimized trusted computing base
(TCB) and only interact with the kernel
in a minimal and safe way. 

Our evaluation results have shown that Lind is least likely to trigger
historically reported kernel bugs, compared against
other systems built without using our metric, such as VirtualBox and
Graphene. The successful implementation of Lind
suggests that new designs using our metric are likely to lead to more
secure systems. 
